---
title: "R Programming A-Z"
author: "Elton Dantas de Oliveira Mesquita"
output: html_document
---


### 1. The Law of Large Numbers

  Test the Law of Large Numbers for N random normally distributed numbers with mean = 0 and sd = 1:
  - Create an R script that will count how many of these numbers fall between -1 and 1 and divide by the total quantity of N;
  - You know that E(X) = 68.2;
  - Check that mean(Xn) -> E(X) as you rerun your script while increasing N.
  
```{r}
lawLargeNum = function(n){
  count = 0
  for(i in rnorm(n)){
    if(-1 < i & i < 1){
      count = count+1
    }
  }
  count/n * 100
}

lawLargeNum(10)
lawLargeNum(100)
lawLargeNum(1000)
lawLargeNum(10000)
lawLargeNum(100000)
```


### 2. Financial Statement Analysis

  Scenario: You are a data scientist working for a consulting firm. One of your colleagues from the Auditing department has asked you to help them assess the financial statement of organisation X. You have been supplied with two vectors of data: monthly revenue and monthly expenses for the financial year in question. Your task is to calculate the following financial metrics:
  a) profit for each month;
  b) profit after tax for each month (the tax rate is 30%);
  c) profit margin for each month (equal to profit after tax divided by revenue);
  d) good months (where the profit after tax was greater than the mean of the year);
  e) bad months (where the profit after tax was less than the mean of the year);
  f) the best month (where the profit after tax was max for the year);
  g) the worst month (where the profit after tax was min for the year).
  All results need to be presented as vectors.
  Results for dollar values need to be calculated with \$0.01 precision, but need to be presented in Units of \$1,000 with no decimal points.
  Results for the profit margin ratio need to be presented in Units of % with no decimal points.
  NOTE: Your colleague has warned you that it is okay for tax for any given month to be negative (in accounting terms, negative tax translates into a deferred tax asset).

```{r}
#Data

revenue = c(14574.49, 7606.46, 8611.41, 9175.41, 8058.65, 8105.44, 11496.28, 9766.09, 10305.32, 14379.96, 10713.97, 15433.50)

expenses = c(12051.82, 5695.07, 12319.20, 12089.72, 8658.57, 840.20, 3285.73, 5821.12, 6976.93, 16618.61, 10054.37, 3803.96)


#Solution

#a)
profits = revenue - expenses
profits

#b)
profits_after_tax = round(profits * 0.7, 2)
profits_after_tax

#c)
profit_margins = round(profits_after_tax/revenue, 2) * 100
profit_margins

#d)
mean_pat = mean(profits_after_tax)
mean_pat

good_months = profits_after_tax > mean_pat
good_months

#e)
bad_months = !good_months
bad_months

#f)
best_month = profits_after_tax == max(profits_after_tax)
best_month

#g)
worst_month = profits_after_tax == min(profits_after_tax)
worst_month
```


